### 2017-08-25 Graduate - Introduction to Analysis I/Homework20170822-1.tex
update

\textbf{Solution:}
\bigskip

>>>>

\textbf{Solution:} 
\begin{proof}
\textbf{Uniqueness:} \\
Assume there exists two field isomorphisms $f_1, f_2$ from $\mathcal{F}_1$ onto $\mathcal{F}_2$. Let $E$ is an upper bounded set in $\mathcal{F}_1$, and according to the Completeness Axiom, it's supremum is $e$. Denote $E_1 = f_1(E)\in \mathcal{F}_2, E_2 = f_2(E)\in\mathcal{F}_2$. Then according to properties of isomorphism, $E_1, E_2$ are both upper bounded sets, so they both have supremums, denoted by $e_1, e_2$. Then since the isomorphism preserves the order, we have $f_1(e) = f_2(e) = e_1 = e_2$. Since for each $x\in \mathcal{F}_1$, we can construct a set with $x$ being it's supremum (for example, a sequence converge to $x$), we have $f_1(x) = f_2(x)$. Thus $f_1 = f_2$. \\[5pt]
\textbf{Existence:} \\

\end{proof}
\bigskip
